\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Leah Hartman} \\ \vspace{1pt}
    \small \href{mailto:x@x.com}{\underline{leah.ghartman@gmail.com}} $|$ 
    \href{https://linkedin.com/in/leahghartman}{\underline{linkedin.com/in/leahghartman}} $|$ \href{https://leahghartman.github.io/}{\underline{leahghartman.github.io}}
\end{center}


%-----------EDUCATION AND TRAINING-----------
\section{Education and Training}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Michigan}{Ann Arbor, MI}
      {Doctor of Philosophy in Applied Physics}{Fall 2024 -- Present}

      \vspace{3mm}
      
    \resumeSubheading
      {Western Kentucky University}{Bowling Green, KY}
      {Bachelor of Science in Physics, Minor in Mathematics}{Fall 2020 -- Spring 2024}
      \resumeItemListStart
        \resumeItem{\textbf{GPA}: 4.0/4.0, \textbf{Summa Cum Laude}}
        \resumeItem{\textit{Fall 2020} -- \textit{Fall 2022} was spent as a \textit{non-degree seeking} high school student as part of The Carol Martin Gatton Academy of Mathematics and Science.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Optically-Generated Plasma Lens for Focusing Relativ. Electron Beams}{Jun. 2023 -- Aug. 2024}
      {University of Colorado, Boulder -- Supervised by Dr. Mike Litos}{Boulder, CO}
      \resumeItemListStart
        \resumeItem{Project focused on the development of an optical configuration to generate a plasma lens capable of focusing relativistic electron beams in plasma wakefield accelerators}
        \resumeItem{Created Python code to perform image analysis, including filtering and processing images, to optimize data collection and analysis}
        \resumeItem{Directly contributed to the development of the plasma lens by acquiring expertise in and manipulating diverse optical components, including cylindrical lenses, beam expanders, and visible-diode lasers}
        \resumeItem{Assisted in setting up camera servers on a Linux-based operating system, allowing for possible future ease-of-use of cameras within the lab}
    \resumeItemListEnd

    \vspace{2mm}

    \resumeSubheading
      {Analyzing Rolling Oscillations Along a Cycloidal Ramp}{Mar. 2022 -- May 2024}
      {Western Kentucky University -- Supervised by Dr. Doug Harper and Dr. Ivan Novikov}{Bowling Green, KY}
      \resumeItemListStart
        \resumeItem{Led the development of an experimental setup to study the translational and rotational motion of objects filled with various viscous liquids along a cycloidal ramp}
        \resumeItem{Used CAD software to design and construct infrared photogates using IR phototransistors and LEDs. Housed these photogates within 3D-printed enclosures for data acquisition}
        \resumeItem{Currently leading the project and mentoring two Gatton Academy students}
        \resumeItem{Developed Python code for efficient data analysis and additionally finalizing LabVIEW code for the control and operation of the infrared photogates}
    \resumeItemListEnd

    \vspace{2mm}
      
    \resumeSubheading
      {Demonstration of Stochastic Resonance in a Mechanical Duffing Oscillator}{Mar. 2022 -- May 2023}
      {Western Kentucky University -- Supervised by Dr. Doug Harper and Dr. Ivan Novikov}{Bowling Green, KY}
      \resumeItemListStart
        \resumeItem{A project focused on creating a system exhibiting stochastic resonance and analyzing its response to different levels of external noise}
        \resumeItem{Facilitated data acquisition for another student to demonstrate stochastic resonance, ensuring efficient and accurate data collection}
        \resumeItem{Developed Python code for data analysis, using scientific libraries to calculate the Kramers' rate of the system}
        \resumeItem{Collaborated on troubleshooting and upkeep of the experimental system and LabVIEW code, ensuring smooth operation and data collection}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------TEACHING EXPERIENCE-----------
\section{Teaching Experience}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Physics Tutor}}{Aug. 2022 -- Dec. 2023}

          \vspace{0.5mm}
          
          \begin{enumerate}
              \item The Carol Martin Gatton Academy of Mathematics and Science Physics Tutor (\textit{Aug. 2022 -- May 2023})
                \resumeItemListStart
                    \resumeItem{Courses tutored include: University Physics I, University Physics II}
                    \resumeItem{Responsibilities include: leading University Physics I and II review sessions, aiding with any homework problems, coding problems, test corrections, general classroom content, and any questions students may have.}
                \resumeItemListEnd

              \vspace{2mm}

              \item Western Kentucky University Physics Help Center (\textit{Aug. 2022 -- Dec. 2023})
                \resumeItemListStart
                    \resumeItem{Courses tutored include: University Physics I, University Physics II, Biophysics I, Biophysics II, Modern Physics I, Astronomy of the Solar System, Astronomy of Stellar Systems, Descriptive Astronomy}
                \resumeItemListEnd
          \end{enumerate}

          \newpage
          
      \resumeProjectHeading
          {\textbf{Learning Assistant}}{Aug. 2022 -- Dec. 2023}
          \resumeItemListStart
            \resumeItem{Assisted in teaching introductory physics labs for University Physics I and II}
            \resumeItem{Responsibilities include: assisting the lab instructor, helping students complete experiments, and ensuring they understand the content each week}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Teaching Assistant}}{Jan. 2023 -- Dec. 2023}
          \resumeItemListStart
            \resumeItem{Taught introductory physics labs for University Physics I and II}
            \resumeItem{Responsibilities include: grading weekly lab worksheets and lab reports for each experiment, basic instruction for each experiment, and assisting students in completing lab each week}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------CONFERENCE PRESENTATIONS AND POSTERS-----------
\section{Conference Presentations and Posters}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Hartman, L.}, Guerrero, M., Doss C., Hansel C., Lee V., Litos M., (May 2024). Optically-generated plasma lens for \\
          \qquad focusing relativistic electron beams. Poster presented at the International Particle Accelerator Conference, \\
          \qquad Nashville, TN.}{}
      \resumeProjectHeading
          {\textbf{Hartman, L.}, Guerrero, M., Doss C., Hansel C., Lee V., Litos M., (October 2023). Optically-generated plasma lens for \\
          \qquad focusing relativistic electron beams. Poster presented at the American Physical Society Division of \\
          \qquad Plasma Physics conference, Denver, CO.}{}

      \resumeProjectHeading
          {Guerrero M., \textbf{Hartman, L.}, Doss C., Hansel C., Lee V., Litos M., (October 2023). Underdense passive plasma lens for \\
          \qquad focusing relativistic electron beams. Poster presented at the American Physical Society Division of Plasma \\
          \qquad Physics conference, Denver, CO.}{}

      \resumeProjectHeading
          {\textbf{Hartman, L.}, Harper D., Hebenstiel L., Novikov I., Sherrard S., (April 2023). An analysis of liquid-filled \\
          \quad containers along a curved ramp using the ROL-FC experimental setup. Oral presentation given at the \\ 
          \quad Western Kentucky University Student Scholar Showcase, Bowling Green, KY.}{}

      \resumeProjectHeading
          {Sherrard, S., \textbf{Hartman, L.}, Harper D., Hebenstiel L., Novikov I., (April 2023). Experimental determination of \\
          \qquad coefficients of friction in rolling oscillation of liquid-filled container (ROL-FC) experimental setup \\
          \qquad for generation of cycloid. Poster presentation given at the Western Kentucky University Student \\
          \qquad Scholar Showcase, Bowling Green, KY.}{}\
          
      \resumeProjectHeading
          {\textbf{Hartman, L.}, Harper D., Hebenstiel, L., Novikov I., (November 2022). Experimental setup to study rolling oscillations \\
          \qquad along a curved ramp. Poster presentation given at the Kentucky Academy of Science annual meeting at \\
          \qquad Morehead University, Morehead, KY.}{}
          
      \resumeProjectHeading
          {Alvarez, I., \textbf{Hartman, L.}, Harper D., Hebenstiel, L., Novikov I., (November 2022). Experimental observation of \\
          \qquad bifurcation in a damped driven oscillator. Poster presentation given at the Kentucky Academy of Science \\
          \qquad annual meeting at Morehead University, Morehead, KY.}{}

      \resumeProjectHeading
          {\textbf{Hartman, L.}, Harper D., Hebenstiel, L., Novikov I., (November 2022). Experimental study of Kramers' rate in a \\
          \qquad magnetically-driven duffing oscillator. Poster presentation given at the Southeastern Section of \\
          \qquad the American Physical Society at the University of Mississippi, Oxford, MS.}{}
        
    \resumeSubHeadingListEnd


%-----------AWARDS AND SCHOLARSHIPS-----------
\section{Awards, Honors, and Scholarships}
    \resumeSubHeadingListStart
      \resumeProjectHeading{\textbf{Scholar of the Ogden College of Science and Engineering}}{Spring 2024}

      \vspace{1mm}
      
      \resumeProjectHeading{\textbf{George V. Page Award for Excellence in Scholarship in Physics and Astronomy}}{Spring 2024}

      \vspace{1mm}
      
      \resumeProjectHeading{\textbf{Mitchell Scholars Award}}{Summer 2023}

      \vspace{1mm}

      \resumeProjectHeading{\textbf{Research Experiences for Undergraduates (REU) Selection}}{Spring 2023}

      \vspace{1mm}

      \resumeProjectHeading{\textbf{Henry M. and Zula G. Yarbrough Award in Mathematics}}{Spring 2023}

      \vspace{1mm}

      \resumeProjectHeading{\textbf{Hugh F. and Katherine A. Johnson Mathematics Award}}{Spring 2023}
      
      \vspace{1mm}
      
      \resumeProjectHeading{\textbf{Gatton Academy Cherry Presidential Scholarship}}{Spring 2022 - Spring 2024}

      \vspace{1mm}
          
      \resumeProjectHeading{\textbf{Targeted Gatton and Craft Academy Graduate Scholarship}}{Spring 2022 - Spring 2024}

      \vspace{1mm}
      
      \resumeProjectHeading{\textbf{Faculty-Undergraduate Student Engagement (FUSE) Grant Award}}{Spring 2022 - Spring 2023}
    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS AND ORGANIZATIONS-----------
\section{Certifications and Organizations}
    \resumeSubHeadingListStart
      \resumeProjectHeading{\textbf{Sigma Pi Sigma -- Physics Honors Society}}{Spring 2024}

      \vspace{1mm}
      
      \resumeProjectHeading{\textbf{Mathematica Student Certification}}{Spring 2021}
    \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{T\&N Pools Chemical Technician}}{May 2021 -- September 2022}
          \resumeItemListStart
            \resumeItem{Tested chemical levels and advised customers on ways to chemically-balance their pools}
            \resumeItem{Performed routine maintenance, services, and cleaning on customers' pools including balancing chemicals, vacuuming, and installing covers}
            \resumeItem{Developed a new scheduling system for customer pool services using Python}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Developer Tools}{: Git (-Lab and -Hub), Slurm, GNU/Linux} \\
     \textbf{Frameworks}{: OpenCV, PyTorch, NumPy, Pandas} \\
     \textbf{Technical Languages and Codes}{: Python, C/C++, MATLAB, Mathematica, NI LabVIEW, Java, LaTeX, HiPACE++} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
